### 2020-01-31 wuhan.tex
can't think of a good concluding sentence for the abstract...

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have prioritized their attention to estimating the basic reproductive number \Ro, which is defined as the average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.
Here, we present a novel framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results demonstrate the importance of propagating uncertainties in all three quantities, in particular in the mean generation interval.
We recommend that more efforts should be

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have prioritized their attention to estimating the basic reproductive number \Ro, which is defined as the average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.
Here, we present a novel framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results emphasize the importance of propagating uncertainties in all three quantities, in particular in the shape of the generation-interval distribution.
